\textbf{Designing a Security Management Layer with Copy-on-Write for CDN Assets}

### 2016-03-17 tex/paper.tex
Better Uprise description
Related related technologies to each other

\subsection{About Uprise}
Uprise (formerly known as ESN) is a company based in Uppsala, Sweden. It is an EA studio focusing on
creating great gaming experiences, which means that they are not focused on the actual gameplay, in
contrast to other EA studios like DICE. Currently Uprise has a lot of focus on developing companion
apps and a new form of menu systems.

@@

\subsection{Interaction of Multiple Accesses} \label{sec:multiple_access}
\fix Rename consequence?
\\
As a result of consequence~\ref{eq:contentupdate} and~\ref{eq:containerupdate} in
Section~\ref{sec:conseq} there can be race conditions where the last write wins. This could be
solved by locks or transactions, but as updates are not based on each other, the trade-off for this
inconsistency to scalability and speed is intentional. However, as can also be seen in
consequence~\ref{eq:fileupdate}, if a file is removed from a content that file is not removed from
the set of files, even though its modification process is the last one to write to the content.
This is necessary as a file can be referenced from several content and the removal process can not
atomically ensure that the file is not referred to by another content. This results in a lot of
files in the system which are not referenced from anywhere. This can be solved by either making each
file keep track of how many times it is referred to and also make it possible to check this number
and delete the file in an atomic fashion. An easier approach would be to have a garbage collector
which locks parts of the system momentarily meanwhile it removes files which are not referenced.

@@

\subsection{JPF}
\fix Not sure where to put this section

JPF was used to test the idea and state transitioning of the model. It is a very simplified
version of the real system that still contains all the important Copy-on-Write concepts and the 
assumptions that have been made in the model. This simplified version was then used to automatically
test for unwanted quirks. It is not a proof that the model works, but it is very exhaustive in its
testing.

@@

\subsection{Related Technologies}
\subsubsection{React}
React is a JavaScript library for building user interfaces. React uses both its own virtual DOM and
the browser's normal DOM, this makes it able to efficiently update dynamic web pages after a change
of state through comparing the old virtual DOM with the resulting virtual DOM after the state change
and then only update the browser's DOM according to the delta between the virtual DOMs~\cite{REACT}.
React can be seen as the system for handling views in front-ends implementing a MVC
(Model-View-Controller) architecture.

\subsubsection{Reflux}
Reflux~\cite{REFLUX} is an idea and a simple library of how to structure your application. It
features a unidirectional dataflow (see Figure~\ref{fig:reflux}) which makes it more suitable, than
for example Flux~\cite{FLUX}, when using a functional reactive programming style.

@@

\subsubsection{Scala} 
Scala is a multi-paradigm programming language. It most commonly runs on the JVM and unlike
Java it supports most functional programming features at the same time as it supports 
object-oriented programming~\cite{SCALA}.

\subsubsection{REST} 
REST stands for representational state transfer, it is an architectural idea for writing stateless
services. These services usually use URIs to identify specific resources and HTTP to modify or query
these resources~\cite{REST}.

\subsubsection{MongoDB}
MongoDB is a document-oriented database, which means that it does not have the concept of rows as
normal relational databases has. Instead each entity in the database is stored as a document which
is not fixed to a predefined table structure~\cite{MONGODB}. MongoDB lacks the support for joins to
improve its possibility to scale, which can be a big downside to some applications containing the
need for such logic.

>>>>

\subsection{About Uprise}
Uprise (formerly known as ESN) is a company based in Uppsala, Sweden. It is an EA studio focusing on
creating great gaming experiences, which means that they are not focused on the actual gameplay, in
contrast to other EA studios like DICE. Historically Uprise has developed for example an
application called BattleLog, which is a companion for the BattleField game series. What Uprise is
currently working on is unfortunately classified.

@@

\subsection{Interaction of Multiple Accesses} \label{sec:multiple_access}
As a result of consequence~\ref{eq:contentupdate} and~\ref{eq:containerupdate} in
Section~\ref{sec:conseq} there can be race conditions where the last write wins. This could be
solved by locks or transactions, but as updates are not based on each other, the trade-off for this
inconsistency to scalability and speed is intentional. However, as can also be seen in
consequence~\ref{eq:fileupdate}, if a file is removed from a content that file is not removed from
the set of files, even though its modification process is the last one to write to the content.
This is necessary as a file can be referenced from several content and the removal process can not
atomically ensure that the file is not referred to by another content. This results in a lot of
files in the system which are not referenced from anywhere. This can be solved by either making each
file keep track of how many times it is referred to and also make it possible to check this number
and delete the file in an atomic fashion. An easier approach would be to have a garbage collector
which locks parts of the system momentarily meanwhile it removes files which are not referenced.

@@

\subsection{JPF}
JPF was used to test the idea and state transitioning of the model. It is a very simplified
version of the real system that still contains all the important Copy-on-Write concepts and the 
assumptions that have been made in the model. This simplified version was then used to automatically
test for unwanted quirks. It is not a proof that the model works, but it is very exhaustive in its
testing.

@@

\subsection{Related Technologies}
\subsubsection{React} \label{sec:react}
React is a JavaScript library for building user interfaces. React uses both its own virtual DOM and
the browser's normal DOM, this makes it able to efficiently update dynamic web pages after a change
of state through comparing the old virtual DOM with the resulting virtual DOM after the state change
and then only update the browser's DOM according to the delta between the virtual DOMs~\cite{REACT}.
React can be seen as the system for handling views in front-ends implementing a MVC-like
(Model-View-Controller) architecture. In this work React is used as a part of building the
front-end.

\subsubsection{Reflux} \label{sec:reflux}
Reflux~\cite{REFLUX} is an idea and a simple library of how to structure your application. It
features a unidirectional dataflow (see Figure~\ref{fig:reflux}) which makes it more suitable, than
for example Flux~\cite{FLUX}, when using a functional reactive programming style. Reflux is used
together with React (see Section~\ref{sec:react}) for this implementation to define a structure of
the flow of data and state changes.

@@

\subsubsection{Scala} \label{sec:scala}
Scala is a multi-paradigm programming language. It most commonly runs on the JVM and unlike
Java it supports most functional programming features at the same time as it supports 
object-oriented programming~\cite{SCALA}. Scala is used to program the back-end and the Spray
toolkit (see Section~\ref{sec:spray}) is used with it to simplify the API.

\subsubsection{REST} \label{sec:rest}
REST stands for representational state transfer, it is an architectural idea for writing stateless
services. These services usually use URIs to identify specific resources and HTTP to modify or query
these resources~\cite{REST}.

\subsubsection{Spray} \label{sec:spray}
Spray~\cite{CASBAH} is an open-source toolkit written in Scala and for Scala (see
section~\ref{sec:scala}). It is used to make it easier to build REST/HTTP APIs (see
section~\ref{sec:rest}) and those abilities is what it is used in the implementation (see
section~\ref{sec:api}).

\subsubsection{MongoDB} \label{sec:spray}
MongoDB is a document-oriented database, which means that it does not have the concept of rows as
normal relational databases has. Instead each entity in the database is stored as a document which
is not fixed to a predefined table structure~\cite{MONGODB}. MongoDB lacks the support for joins to
improve its possibility to scale, which can be a big downside to some applications containing the
need for such logic. MongoDB is used as a persistent storage for the back-end to store all the
projects and nodes in the tree structures and also the files uploaded to the system. Scala (see
Section~\ref{sec:scala}) uses a layer called Casbah~\cite{CASBAH} to interface with MongoDB.
